DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The proposed synthesis methodology for closed-loop digital control
systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}; 
it can be split into two main stages as follows: manual (user) and 
automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital Controller Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

In step $1$, the digital-control representation is define, which can be in 
transfer-function or state-space equations. In step $2$, the physical plant 
with the respective coefficients must be designed, according to equations 
(\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, 
the numerical representation for the digital controller implementation must be 
defined, {\it i.e.}, the FWL format that includes the number of bits for the integer 
and fractional parts and the dynamic range inputs. The results from the manual 
procedure is a digital-system implementation for the given physical plant in MATLAB.

The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, 
and then translates it into a ANSI-C program; then in step $B$, the DSSynth Tool is invoked. 
Finally, in step $C$, the digital controller is synthesized based on CEGIS. The output generated 
in MATLAB is the synthesized digital controller, which can be represented in transfer-function 
or state-space format. The synthesis is \emph{successful} if a digital controller is correctly synthesized;
otherwise the synthesis has status \emph{failed} if any parameter is defined incorrectly 
in previous steps, or there is no solution for the designed digital controller.

>>>>

The proposed synthesis methodology for closed-loop digital control
systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}, 
which can be split into two main stages as follows: manual (user) and 
automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
\caption{Digital Controller Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

In step $1$, the user has to define the digital controller representation, 
which can be transfer-function or state-space equations. 
In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
and (\ref{eq:ss-example})) must be designed, using the preferred method 
from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
the numerical representation for the digital controller implementation must be 
defined by the user, {\it i.e.}, the FWL format that includes the number of bits for the integer 
and fractional parts as well as the dynamic range inputs. The result of the manual 
procedure performed by the user is a digital system specification for the given 
physical plant in MATLAB.

After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
specification in MATLAB, and then translates it into an ANSI-C program. 
In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
The output generated by \tool is the synthesized digital controller represented either in transfer-function 
or state-space format. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
synthesized w.r.t. FWL effects; otherwise the synthesis is considered to be \emph{failed}, if any parameter is 
incorrectly defined in previous steps, or if there is no solution (digital controller) for the respective physical plant
 given the digital controller word-length.
